Formulating experimental feeds

### 2025-08-04 05_formulating_feeds.qmd
Diet similarity

feed_inputs <- feed_input_file %>% 
  read_excel(sheet = "all_feeds") %>% 
  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
  mutate(feed = as.factor(feed),
         ingredient = as.factor(ingredient)) %>% 
  merge(ingreds, by = "ingredient", all = T)

@@

>>>>

feed_inputs <- feed_input_file %>% 
  read_excel(sheet = "all_feeds") %>% 
  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
  mutate(feed = as.factor(feed),
         ingredient = as.factor(ingredient)) %>% 
  merge(ingreds, by = "ingredient")

@@

# Similarity

For later - how similar are the diets?

```{r}
#| label: diet-similarity

feed_simil <- feed_inputs %>% 
  select(ingredient, feed, proportion) %>% 
  as.data.frame() %>% 
  pivot_wider(
    names_from = feed,
    values_from = proportion,
    id_cols = ingredient,
    values_fn = as.numeric
  ) %>% 
  mutate(
    diff_PD_MD = abs(marine_dominant - plant_dominant),
    diff_PD_NI = abs(novel_inclusive - plant_dominant)
  )

1 - sum(feed_simil$diff_PD_MD, na.rm = T)
1 - sum(feed_simil$diff_PD_NI, na.rm = T)
```
